---
title: "Analysis of Spanish Erasmus students"
author: "Nico Dehnert, Kacper Rozenbaum"
date: "15 June 2016"
runtime: shiny
output: html_document
---

```
```{r echo=FALSE, eval=TRUE, tidy=TRUE}
#stuff to load
if (0){
  install.packages("plyr")
  install.packages("RCurl")
  install.packages("GISTools")
  install.packages("maps")
  install.packages("mapdata")
  install.packages("maptools")
  install.packages("mapdata")
  install.packages("mapplots")
  install.packages("scales")
  install.packages("mapproj")
}

library(plyr)
library(RCurl)
library(GISTools)
library(maps)
library(mapdata)
library(maptools)
library(mapdata)
library(mapplots)
library(scales)
library(mapproj)

ProjectData <- read.csv("Erasmus.csv", header = TRUE)

student_age <- ProjectData$AGE

cities <- ProjectData$City

AgeNormDistribution <- dnorm(student_age)

city_count <- count(cities)

city_count_sorted <- city_count[order(city_count[["freq"]], decreasing = TRUE),]

top5cities <- head(city_count_sorted)

```

Basic statistics of age of Erasmus students: 


```{r echo=FALSE, eval=TRUE, tidy=TRUE}

age_summary <- summary(student_age)
print(age_summary)

```


Histogram of age of Erasmus students:
```{r echo=FALSE, eval=TRUE, tidy=TRUE}

age_hist <- hist(student_age, xlab = "Age of students", main = "Histogram of students' age", ylab = "Number of students", xlim = c(18,30), freq = 1, breaks = 49)
```

Basic statistics of years of higher education of Erasmus students:
```{r echo=FALSE, eval=TRUE, tidy=TRUE}
eduYears_summary <- summary(ProjectData$Years_Higher_Education)
print(eduYears_summary)
```

Histogram of years of higher education


```{r echo=FALSE, eval=TRUE, tidy=TRUE}

hist(ProjectData$Years_Higher_Education, xlab = "Years of higher education", main = "Histogram of years of higher education", ylab = "Number of students", xlim = c(0,10), freq = 1, breaks = 20, col = "lightblue")
```

Top 5 universities sending students to Erasmus exchange
```{r echo=TRUE, eval=FALSE, tidy=TRUE}

barplot(top5cities$freq, main = "Top 5 universities", xlab = "University", ylab = "Students" , names.arg = top5cities$x, col = "darkblue", cex.names = 0.4)

```

Top 6  universities by number of Erasmus students - visualization:
```{r echo=FALSE, eval=TRUE, tidy=TRUE}
add.alpha(brewer.pal(5,'Reds'),0.5)


myColours = c(1, "steelblue", "#FFBB00", rgb(0.4, 0.2, 0.3))
myColoursAlpha <- add.alpha(myColours, alpha=0.4)

map("worldHires","Spain", xlim=c(-10,5),ylim=c(35,45), col="gray90", fill=TRUE)




add.pie(z=c(1), x=-3.45, y=40.25, radius=1.5, labels = "Madrid1 (4480)", border = NULL, edges = 200, clockwise = TRUE, col = "#A50F1580")

add.pie(z=c(1), x=2.1, y=41.21, radius=1.7, labels = "Barcelona (4255)", border = NULL, edges = 200, clockwise = TRUE, col = "#A50F1580")

add.pie(z=c(1), x=-3.35, y=37.1, radius=0.5, labels = "Granada (1934)", border = NULL, edges = 200, clockwise = TRUE, col = "#A50F1580")

add.pie(z=c(1), x=-2.56, y=43.16, radius=0.27, labels = "Bilbao (1493)", border = NULL, edges = 200, clockwise = TRUE, col = "#A50F1580")

add.pie(z=c(1), x=-3.45, y=40.25, radius=0.24, labels = "Madrid2 (1445)", border = NULL, edges = 200, clockwise = TRUE, col = "#A50F1580")

add.pie(z=c(1), x=-4.23, y=36.43, radius=0.03, labels = "Malaga (1036)", border = NULL, edges = 200, clockwise = TRUE, col = "#A50F1580")

```
